method

### 2022-01-28 06_Paper/ER-ED/method.Rmd
renamed chunk

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

All statistical analyses were perfomed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2020] for Windows.
The level of significance was set to $\alpha$ = .05.

>>>>

```{r SetupMethod, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

All statistical analyses were perfomed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2021] for Windows.
The level of significance was set to $\alpha$ = .05.
